Hurricane Evacuation Strategies for the State of Mississippi

### 2015-11-16 manuscript.tex
Added some shit

  \par The interesting part, though, is that this information tells us where the bottleneck is in terms of transportation. By inspection, we can see that a new road linking counties 20 and 56 (George to Perry) could increase the maximum flow number, as well as push the congestion areas further north (which means people can get further away from the hurricanes faster).

@@

        t^* &= \frac{616338}{27000}\\
        t^* &= 10 \text{hrs}

@@

@@

>>>>

  \par The interesting part, though, is that this information tells us where the bottleneck is in terms of transportation. By inspection, we can see that a new road linking counties 20 and 56 (George to Perry, located on the south east corner of the state) could increase the maximum flow number, as well as push the congestion areas further north (which means people can get further away from the hurricanes faster). 

@@

        t^* &= \frac{532480}{21000}\\
        t^* &= 25 \text{hrs}

@@

    So according to this model, if we decided to evacuate everyone in the southern counties all at once, it would take upwards of a day to get everyone to safe counties.

@@

    % TODO
